\documentclass[12pt,english]{moderncv}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{babel}

% \usepackage{bookmark}


\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\moderncvtheme[green]{casual}
% possible themes are "classic" and "casual"
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% required
\firstname{Oscar David\\}
% required
\familyname{Arbel\'aez Echeverri}

% optional, remove the line if not wanted
\title{Curriculum Vitae}

% optional
% \address{street and number}{postcode city}
% '\\' adds a line break
\address{Carrera 23  \#55A--35}{Manizales, Colombia}

% optional
% \phone{+57(6) 890 6069}
% optional
\mobile{+57 313 712 5660}
% optional
%\fax{+43(0)999 7777}
% optional
\email{odarbelaeze@unal.edu.co}
% optional
\extrainfo{%
    \href{https://github.com/odarbelaeze}{github.com/odarbelaeze}
}

% optional
% \photo[height]{name}
% 'height' is the height the picture is resized to
% 'name' is the name of the picture file
% \photo[64pt]{CV-image}

% optional
% \quote{"Everyone wants to be in the upper hand."}

\makeatother

\providecommand{\LyX}{\texorpdfstring%
  {L\kern-.1667em\lower.25em\hbox{Y}\kern-.125emX\@}
  {LyX}}

\newcommand*{\cvreference}[7][.25em]{%
    \cvitem[#1]{}{%
    \ifthenelse{\equal{#2}{}}{}{\textbf{#2}\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{\addresssymbol~#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\href{mailto:#6}{\texttt{#6}}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}
}}


\begin{document}

\maketitle

\begin{centering}
    The source and support documents for the present resume are available at
    \url{https://github.com/odarbelaeze/resume}, feel free to ask for
    additional support documents if some are missing.
\end{centering}


\section{Education}

\cventry{2012--2016}
        {Master in Science --- Physics}
        {Universidad Nacional de Colombia}
        {Manizales}
        {Colombia}
        {%
            I developed the master thesis entitled `Monte Carlo simulation of
            bit patterned media applied to data storage devices' that involved
            the understanding of modern hard disk drive technology and
            simulation of magnetic materials and produced a new model for bit
            patterned media which is the next step in order to improve magnetic
            storage density.
        }

\cventry{2008--2012}
        {Bachelor of Science in Engineering Physics}
        {Universidad Nacional de Colombia}
        {Manizales}
        {Colombia}
        {}


\section{Research~papers}

\cventry{March 2018}
        {Atomistic modelling of magnetic nano-granular thin films}
        {Physica E:\@ Low-dimensional Systems and Nanostructures}
        {Elsevier}
        {}
        {DOI:\@ \href{https://doi.org/10.1016/j.physe.2017.11.017}{10.1016/j.physe.2017.11.017}}

\cventry{February 2017}
        {%
            Spontaneous Perpendicular Anisotropy in Ultra-thin Ferromagnetic
            Films
        }
        {Journal of Superconductivity and Novel Magnetism}
        {Springer}
        {}
        {DOI:\@ 10.1007/s10948--017--4005--9}

\cventry{February 2017}
        {%
            Surface anisotropy and particle size influence on hysteresis loops
            in La2/3Ca1/3MnO3 nanoparticles: A simulation approach
        }
        {Journal of Magnetism and Magnetic Materials}
        {Elsevier}
        {}
        {DOI:\@ 10.1016/j.jmmm.2016.10.108}

\cventry{June 2016}
        {%
            Implementation details of a variational method to solve the time
            independent Schrödinger equation.
        }
        {Revista mexicana de física E}
        {Sociedad mexicana de física}
        {}
        {}

\cventry{December 2015}
        {Atomistic Simulation of static magnetic properties of bit patterned media}
        {Physica E}
        {Elsevier}
        {}
        {DOI:\@ 10.1016/j.physe.2015.12.016}

\cventry{October 2014}
        {%
            Simulation of magnetotransport properties of
            ferromagnetic/antiferromagnetic multilayers of manganites
        }
        {Journal of Superconductivity and Novel Magnetism}
        {Springer}
        {}
        {DOI:\@ 10.1007/s10948--014--2827--2}


\section{Experience}

\cventry{Apr. 2016\\--current}
        {Full stack software engineer}
        {BairesDev}
        {}
        {}
        {%
            I deliver full stack contractor software engineering services to
            \href{https://www.adroll.com/}{AdRoll} through
            \href{http://www.bairesdev.com/}{BairesDev}. My responsibilities
            include writing and maintaining code that allows advertisers to run
            native ad campaigns through AdRoll, both in the backend and
            frontend.
        }

\cventry{Feb. 2016\\--May. 2017}
        {University professor}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            I deliver on-site courses for the department of exact and natural
            sciences at the Universidad Nacional de Colombia. I delivered
            Simulation 1 for Engineering Physics in the first term of 2016, and
            Informatics 3 for Engineering Physics in the second term of 2016
            and in the first term of 2017.
        }

\cventry{Mar. 2015\\--Mar. 2016}
        {Scientific technology consultant}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            Mainly I had to give advice and aid the process of purchasing a
            small high performance computing cluster for a research group in
            the Department of Physics of the university, furthermore I had to
            install the cluster out of the bare bone servers in order to
            optimize the cost and perform maintenance operations. Furthermore,
            my responsibilities included teaching people how to take advantage
            of the cluster and to build a website to improve communication
            within and outside the research group. The main accomplishment I
            achieved during this time was to have a 100\% occupancy in the
            cluster for several months.
        }

\cventry{Jul. 2016\\--Aug. 2016}
        {Summer intern}
        {Computational Magnetism Group, University of York}
        {United Kindom}
        {}
        {%
            In this internship I had the responsibility giving the finishing
            touches and benchmark the CUDA support module for the
            \textsc{Vampire} physics simulation code. The code is available
            at \url{http://vampire.york.ac.uk/}.
        }

\cventry{May. 2015\\--Jul. 2015}
        {Summer intern}
        {Computational Magnetism Group, University of York}
        {United Kindom}
        {}
        {%
            In this internship I had the responsibility of leading a small
            development team and code in order to add a new feature to the
            \textsc{Vampire} physics simulation code. The challenge of the
            project was to integrate CUDA support into a mainly serial and MPI
            C++ codebase. The feature is still in PR waiting for polising and
            approval \url{https://github.com/richard-evans/vampire/pull/4}
        }

\cventry{May. 2015\\--Jul. 2015}
        {Project: Web tools for smart selection of scientific articles applying network analysis}
        {Tree of Science}
        {}
        {}
        {%
            For this job I had a managerial position where I had to lead a
            small development team in order to deliver a production version of
            the Tree of Science tool now hosted at
            \url{http://tos.manizales.unal.edu.co}.
        }

\cventry{Sept. 2014\\--Feb. 2015}
        {Project: Web tools for smart selection of scientific articles applying network analysis}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            I aided the research and analysis of network algorithms (graph
            algorithms) and indicator definition. I also helped in the design
            and delivery of a workshop on scientific data analysis with python.
            The main product was a working prototype of the tool called Tree of
            Science (ToS), which aims to deliver guidance to both young and
            experienced scientist about the scientific literature they should
            read in order to understand a topic.
        }

\cventry{Feb. 2013\\--Feb. 2015}
        {Scholarship holder}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            I was awarded and scholarship and worked as a novice researcher in
            the academic work-group PCM Computational Applications.
        }

\cventry{Aug. 2013\\--Dec. 2016}
        {IT Consultant}
        {Fundación Alas de Cristal}
        {}
        {}
        {%
            My responsibilities were to deliver and maintain the website of the
            foundation and to facilitate the relationship of the foundation
            with other businesses in the IT sector.
        }

\cventry{Jul. 2013\\--Sept. 2013}
        {Web developing volunteer staff}
        {Universidad de Caldas}
        {}
        {}
        {%
            I developed the website for the 2013 book fair of Manizales
            \textit{(Feria del Libro de Manizales)} I worked together with a
            designer of the university to get the best product we could with
            the smallest set of assets.
        }

\cventry{Jan. 2013\\--Sept. 2013}
        {Technical Chair Assistant}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            I helped with the organization of the 5th Latin-American Conference
            in Networked Electronic Media (LACNEM). In particular, I supported
            the technical chair of the conference with the development of the
            conference's website.
        }

\cventry{Oct. 2012\\--Feb. 2013}
        {Intern}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            In this internship, I developed some scientific software, mostly
            python scripts and implemented Monte Carlo algorithms using Fortran
            and C++. I used those scripts and programs to perform atomistic
            simulations of magnetic materials.
        }

\cventry{Aug. 2009\\--May 2011}
        {Intern}
        {Universidad Nacional de Colombia}
        {}
        {}
        {%
            I performed as a teaching assistant in the course practice of
            Mechanical Physics, Physics of electricity and magnetism, Cellular
            Biology, and Physics of Waves and Oscillations.
        }


\section{Languages}

\cvlanguage{Spanish}
           {Native}
           {}

\cvlanguage{English}
           {Near-Native}
           {%
               MET, Score: 119 (B2 Listening --- C1 Reading and Grammar)\\
               Berlitz, Accumulated Score: B2\\
               I have improved a lot since my last exam
           }

\section{Computer~skills}

\cvcomputer{OS}            {Linux\\Windows\\MacOS}
           {Admin}         {AWS\\Docker\\Nginx}

\cvcomputer{Programming}   {Rust\\C/C++\\Python\\JavaScript}
           {Automation}    {Autotools\\Dist Utils\\Unittest\\Gulp\\CMake}

\cvcomputer{Scientific}    {NumPy\\SciPy\\Matplotlib\\Bokhe\\Pandas}
           {Typography}    {pandoc\\markdown\\\LaTeX{}\\\LyX{}}


\cvcomputer{Web~design}    {React\\ES6\\HTML5\\sass}
           {Backend}       {Flask\\Django}


\section{Event~Participation}

\cventry{December\\2017}
        {CODATA-RDA School on Data Science}
        {CODATA, Research Data Aliance, ICTP-SAIFR, Universidade Estadual Paulista}
        {São Paulo, Brasil}
        {Nov 30 --- Dec 16, 2017}
        {(Helper)}

\cventry{July\\2017}
        {2017 CODATA-RDA Research Data Science Summer School}
        {CODATA, Research Data Aliance, Abdus Salam International Centre for Theoretical Physics}
        {Trieste, Italy}
        {July 10 --- 28, 2017}
        {(Participant)}

\cventry{July\\2015}
        {20th International conference on magnetism}
        {Club español de magnetismo}
        {Barcelona, Spain}
        {July 5 --- 10, 2015}
        {(Poster contributor)}

\cventry{May\\2015}
        {Workshop on accelerated high performance computing in computational sciences}
        {Abdus Salam International Centre for Theoretical Physics}
        {Trieste, Italy}
        {May 25 --- June 5, 2015}
        {(Participant)}

\cventry{September\\2014}
        {2nd Workshop on Statistical Physics}
        {Universidad de los Andes, Universidad Nacional de Colombia}
        {Bogotá, Colombia}
        {September 22 --- 26, 2014}
        {(Oral Contributor)}

\cventry{September\\2014}
        {2nd Workshop on Statistical Physics}
        {Universidad de los Andes, Universidad Nacional de Colombia}
        {Bogotá, Colombia}
        {September 22 --- 26, 2014}
        {(Oral Contributor)}

\cventry{March\\2014}
        {LAMMPS Users and Developers Workshop and Symposium}
        {Abdus Salam International Centre for Theoretical Physics}
        {Trieste, Italy}
        {March 10 --- 21, 2014}
        {(Participant)}

\cventry{March\\2014}
        {%
            Advanced Techniques for Scientific Programming and Management
            of Open Source Software Packages
        }
        {Abdus Salam International Centre for Theoretical Physics}
        {Trieste, Italy}
        {March 24 --- 28, 2014}
        {(Participant)}

\cventry{September\\2013}
        {5th Latin American Workshop on Networked Electronic Media}
        {Universidad Nacional de Colombia}
        {Manizales, Colombia}
        {September 2 --- 4, 2013}
        {(Organizer)}


\cventry{September\\2013}
        {1st Workshop on Applied Mathematics --- Region Cafetera}
        {Universidad Nacional de Colombia}
        {Manizales, Colombia}
        {September 2 --- 4, 2013}
        {(Organizer)}

\cventry{September\\2012}
        {III Congreso Nacional de Ingeniería Física}
        {EAFIT University}
        {Medellín, Colombia}
        {September 10 --- 14, 2012}
        {(Oral contributor)}

\cventry{February\\2012}
        {Seminario Internacional de Ingeniería Biomédica (SIB2012)}
        {Universidad de los Andes}
        {Bogotá, Colombia}
        {September 10 --- 14, 2012}
        {(Participant)}

\cventry{September\\2010}
        {II Congreso Nacional de Ingeniería Física}
        {Universidad Tecnol\'ogica de Pereira}
        {Pereira, Colombia}
        {September 6 --- 10, 2010}
        {(Participant)}

\cventry{July\\2010}
        {IX Latin American Workshop on Magnetism, Magnetic Materials and their Applications}
        {Universidad Nacional de Colombia}
        {Manizales, Colombia}
        {July 26 --- 30, 2010}
        {(Participant)}

\cventry{July\\2010}
        {IX Latin American School on Magnetism}
        {Universidad Nacional de Colombia}
        {Manizales, Colombia}
        {July 21 --- 24, 2010}
        {(Participant)}


\section{Complementary~Education}

\cventry{Spring\\2018}
        {Software carpentry instructor certification}
        {}
        {Software carpentry}
        {Erin Becker}
        {April 9, 2018}

\cventry{Fall\\2013}
        {Machine Learning}
        {}
        {Coursera}
        {Associate Professor Andrew Ng, Computer Science Department, Stanford University}
        {November 12, 2013}

\cventry{Fall\\2013}
        {HTML5 Game Development}
        {Building High Performance Web Applications}
        {Udacity}
        {Peter Lubbers and Colt McAnlis}
        {November 8, 2013}

\cventry{Summer\\2013}
        {Curso Introductorio a la Simulación Monte Carlo}
        {Monte Carlo Simulation, Introductory Course}
        {Universidad Católica de Pereira}
        {}
        {September 11--11, 2013}

\cventry{Spring\\2013}
        {Computer Science 101}
        {}
        {Coursera}
        {Nick Parlante, Lecturer in Computer Science, Stanford University}
        {May 13, 2013}

\cventry{Fall\\2011}
        {Estructura del lenguaje de programación C++ (Nivel II)}
        {C++ programming language structure (Level II)}
        {Servicio Nacional de Aprendizaje, SENA}
        {}
        {November 23, 2011}

\cventry{Summer\\2011}
        {Metrología: Patrones, instrumentos y tolerancias}
        {Metrology: Patterns, instruments and allowances}
        {Servicio Nacional de Aprendizaje, SENA}
        {}
        {November 23, 2011}

\cventry{Spring\\2011}
        {Estructura del lenguaje de programación C++ (Nivel I)}
        {C++ programming language structure (Level I)}
        {Servicio Nacional de Aprendizaje, SENA}
        {}
        {March 18, 2011}


\section{Achievements}

\cventry{2016}
        {Distinción meritoria en tesis de posgrado}
        {Honor distinction in postgraduate thesis}
        {Universidad Nacional de Colombia}
        {}
        {(awarded by the faculty council, after being recommended by the thesis referees)}

\cventry{2013}
        {Beca Grado de Honor de Pregrado}
        {Honor Degree Scholarship}
        {Universidad Nacional de Colombia}
        {}
        {}

\cventry{2012}
        {Grado de Honor}
        {Honor Degree}
        {Universidad Nacional de Colombia}
        {}
        {}


\cventry{2009 --- 2011}
        {Exención de pago de derechos académicos}
        {Exemption from payment of academic fees}
        {Universidad Nacional de Colombia}
        {}
        {(earned two times in 2009, as well as in 2010 and 2012)}


\cventry{2007}
        {Decreto de Honores No. 0787}
        {Honors Act No. 0787}
        {Gobernacíon de Caldas}
        {December 6th, 2007}
        {(earned each year by the ten best Students, Teachers, and Teaching institutions in Caldas)}


\cventry{2007}
        {Orden José Joaquin Montes}
        {Order of José Joaquin Montes}
        {Manzanares (Caldas, Colombia) Majorship}
        {December 1st, 2007}
        {(earned each year by the best student graduating from high school in Manzanares)}


\section{References}


\cvreference%
        {Prof.~Elisabeth Restrepo Parra}
        {Departamento de Ciencias Exactas y Naturales}
        {Universidad Nacional de Colombia}
        {Carrera 27 \# 64--60, Manizales, Colombia}
        {erestrepopa@unal.edu.co}
        {+57 321 700 4351}


\cvreference%
        {Ivan Girotto}
        {Information \& Communication Technology Section}
        {The Abdus Salam-International Centre for Theoretical Physics}
        {Strada Costiera, 11 --- I--34151, Trieste, Italy}
        {igirotto@ictp.it}
        {+39 040 2240 484}


\cvreference%
        {Dr.~Axel Kohlmeyer}
        {Institute for Computational Molecular Science (035--07)}
        {College of Science and Technology, Temple University}
        {Philadelphia, PA 19122}
        {akohlmey@gmail.com}
        {+1 215 204 4218}


\cvreference%
        {Dr.~Richard F. L. Evans}
        {The Department of Physics}
        {University of York}
        {YO10 5DD, York, UK}
        {richard.evans@york.ac.uk}
        {+44 (0)1904 322822}


\end{document}
